Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-12 surfaces-write-up/surface-write-up.tex
fix todo, missing }, delete some old macros

\DeclareMathOperator\di{Div}
\newcommand\bida{a}
\newcommand\bidb{b}
\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand{\halfcan}{L}
\DeclareMathOperator{\supp}{Supp}
\DeclareMathOperator{\initial}{in_\prec}
\DeclareMathOperator{\gin}{gin}
\DeclareMathOperator{\Eff}{Eff}
\DeclareMathOperator{\sat}{sat}
\DeclareMathOperator{\newspan}{span}
\DeclareMathOperator{\proj}{Proj}
\DeclareMathOperator{\spec}{Spec}
%\captionsetup[table]{belowskip = 4pt}

@@

\todo{define bidegrees a_i and b_i}
\end{prop}

@@

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $F_{\vec{v}^{d_i} := \frac{u^{d_i}
x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
relations of the form
\[
	F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}} = F_{d_k}^{\vec{y}} F_{d_\ell}^{\vec{z}}
\]

>>>>

\DeclareMathOperator\di{Div}
\newcommand\bida{a}
\newcommand\bidb{b}

\DeclareMathOperator{\supp}{Supp}
\DeclareMathOperator{\initial}{in_\prec}
\DeclareMathOperator{\gin}{gin}
\DeclareMathOperator{\Eff}{Eff}
\DeclareMathOperator{\sat}{sat}
\DeclareMathOperator{\newspan}{span}
\DeclareMathOperator{\proj}{Proj}
\DeclareMathOperator{\spec}{Spec}
%\captionsetup[table]{belowskip = 4pt}

@@

\todo{define bidegrees $a_i$ and $b_i$}
\end{prop}

@@

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $F_{\vec{v}}^{d_i} := \frac{u^{d_i}
x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
relations of the form
\[
	F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}} = F_{d_k}^{\vec{y}} F_{d_\ell}^{\vec{z}}
\]
